Kyoto VR MQP Paper First Draft

### 2019-09-22 paper.tex
add more testing

\subsection{Testing ARuko}
\label{sec:aruko}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{turtle-burger.jpg}
	\caption[A rare but delicious turtle burger in the wild]{A rare but
		delicious turtle burger in the wild~\autocite{harvey2002}.}
	\label{fig:turtleBurger}
\end{figure}

>>>>

Because the Editour is intended only to be a tool to aid Atticus in creating
tours, not an application for the general public, our user testing of it was less
rigid.

\subsubsection{Unit Testing the Editour Backend}
\label{sec:unitTestingTheEditourBackend}

To test the API and backend of the Editour web app we used the Mocha testing
framework. Mocha is the most depended-upon package in the Node Package
Manager~\autocite{tidelift2019}, and is widely used by professional software
development teams. It has a myriad of useful features that allow developers to
quickly write unit tests for complex Node.js projects~\autocite{mochajs2019}.
Most importantly for us, it has good support for testing asynchronous JavaScript
functions, since most of the backend is written asynchronously. Along with Mocha
we also used SuperTest, a library for writing high-level end-to-end HTTP
tests~\autocite{supertest2019}.

For each of the six API endpoints that the backend responds to we wrote an
extensive series of end-to-end tests to ensure that each step along the pipeline
from receiving a request to sending a response worked properly. We also wrote
many fuzz tests, to make sure the backend would respond correctly to invalid
requests, e.g. by responding with an HTTP 400 error message~\autocite{rfc7231}.

These tests were very useful in tracking down bugs and unexpected behavior in
the backend, and also allowed us to make sure no functionality changed when
adding new features or making changes to underlying logic later on.

\subsection{Frontend Web Application Testing}
\label{sec:frontendWebApplicationTesting}

\subsection{Testing ARuko}
\label{sec:testingARuko}

@@

% \begin{figure}[h]
%	\centering
%	\includegraphics[width=\textwidth]{turtle-burger.jpg}
%	\caption[A rare but delicious turtle burger in the wild]{A rare but
%		delicious turtle burger in the wild~\autocite{harvey2002}.}
%	\label{fig:turtleBurger}
%\end{figure}
